```{r}
#| include: false
library(htmltools)

screenshot <- function(name, alt) {
  tags$picture(
    tags$source(
      media = "(prefers-color-scheme: dark)",
      srcset = paste0("images/", name, "-dark.png")
    ),
    tags$img(src = paste0("images/", name, "-light.png"), alt = alt)
  )
}
```

# basecoat

<!-- badges: start -->
[![R-CMD-check](https://github.com/ricochet-rs/basecoat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ricochet-rs/basecoat/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Bindings to the [basecoat UI](https://basecoatui.com/) component library from R.

Basecoat is a pure tailwind css implementation of [shadcn/ui](https://ui.shadcn.com/) that is the very same design system that powers [ricochet.rs](https://ricochet.rs). Naturally, we've grown quite fond of it.

## Installation

```r
pak::pak("ricochet-rs/basecoat")
```

## Usage

`{basecoat}` is designed as an `htmltools` package that generates raw HTML with _opt-in_ shiny binding.

It works for creating HTML templates or with server-side-rendering (SSR) with a framework like `{plumber2}` or `{ambiorix}` as well as an opt-in [`{shiny}`]() integration.


## Page Layouts

To help create full page applications, two page layout helps are shipped:

- `bc_page_navbar()`
- `bc_page_sidebar()`


## Shiny integration

{basecoat} ships an optional shiny integration.

```{r}
#| echo: false
#| output: asis
screenshot(
  "shiny-app",
  "A Shiny app using bc_page_sidebar(), with basecoat inputs wired to input$"
)
```

Open an example application file with:

```{r}
#| eval: false
tmp <- tempfile(fileext = ".R")
fp <- system.file("examples", "shiny-app.R", package = "basecoat")
file.copy(fp, tmp)

file.edit(tmp)
```

## Theme builder

`bc_theme_builder()` can be used to launch a small html page to customize your own theme. Alternatively, you can use the theme customization in the [package docs](https://ricochet-rs.github.io/basecoat/theme/index.html) to help

```{r}
#| eval: false
bc_theme_builder()
```

```{r}
#| echo: false
#| output: asis
screenshot("ricochet-theme", "The theme builder on the ricochet style pack")
```


```{r}
#| echo: false
#| output: asis
screenshot(
  "random-theme",
  "The same page after deriving a palette from a new primary colour"
)
```
