---
title: "Theming"
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

## Create a theme

Open the [online theme builder](../theme/index.html), or run it locally:

```{r}
#| eval: false
bc_theme_builder()
```

Select **CSS** to save `theme.css`.
The file contains only the `:root` and `.dark` token blocks.

You can also use [tweakcn](https://tweakcn.com/).
Select **Code** and save the CSS as `theme.css`.
It works with `bc_theme()` unedited.

## Load your theme

Call `bc_theme()` after `bc_deps()`:

```{r}
#| eval: false
htmltools::tagList(
  bc_deps(),
  bc_theme("theme.css"),
  bc_button("Save")
)
```

Use the `theme` argument of `bc_deps()` to do both in one call:

```{r}
#| eval: false
bc_deps(theme = "theme.css")
```

If your theme uses additional web fonts, those need to be imported manually.

## Further theme customization

If further customization of a theme is necessary, it should be done in the `theme.css` file for styling tokens.
Additionally, if you need to modify the components wholesale, it should be done via `@apply` directives using utility classes.

## Add your own classes

You can write your own classes in `theme.css` using Tailwind's `@apply` directive.
Classes written this way go inside of `@layer components`:

```css
@layer components {
  .btn-pill {
    @apply rounded-full;
  }
}
```

Browsers don't understand `@apply`.
Because `bc_theme()` gives the browser the file as-is, Tailwind has to compile the file first.
Compiling turns each `@apply` into regular CSS.

For Tailwind to know what `rounded-full` means, the first line of `theme.css` must be this:

```css
@reference "tailwindcss";
```

The `@reference` line lets Tailwind look up the utilities without copying all Tailwind's own styles into your file.
A theme exported from tweakcn starts with `@import "tailwindcss";`, so replace that line with `@reference "tailwindcss";`.
A theme from the theme builder has no such line, so add it.

Compile the file with the [Tailwind CLI](https://tailwindcss.com/docs/installation/tailwind-cli):

```bash
npm install tailwindcss @tailwindcss/cli
npx @tailwindcss/cli -i theme.css -o theme.min.css
```

Then load `theme.min.css` with `bc_theme()` instead of `theme.css`, and pass the class to a component:

```{r}
#| eval: false
htmltools::tagList(
  bc_deps(),
  bc_theme("theme.min.css"),
  bc_button("Save", class = "btn-pill")
)
```

## Style packs

These are the bundled style packs:

```{r}
bc_styles
```

To use a style pack, set the `style` argument of `bc_deps()`:

```{r}
#| eval: false
bc_deps(style = "lyra")
```
