---
title: "Theming"
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

```{r}
#| label: setup
#| include: false
library(basecoat)
```

## Pick a pack

```{r}
bc_styles
```

```{r}
#| eval: false
bc_deps(style = "maia")
```

**Once per page.** A second call is deduplicated and one wins.

## Dark mode

```{r results="asis"}
bc_theme_switcher()
```

**Flips the `dark` class on `<html>`.** The choice survives a reload.

## Override tokens

```css
:root { --primary: oklch(0.54 0.16 320); --radius: 0.25rem; }
.dark { --primary: oklch(0.72 0.14 320); }
```

```{r}
#| eval: false
bc_deps(style = "vega", theme = "my-theme.css")
```

**Loads after the pack, so it wins.** Names are shadcn/ui: `--background`, `--foreground`, `--primary`, `--border`, `--ring`, `--radius`.

**`--radius` drives every corner.** The pack still owns layout.

## tweakcn

**Paste an export in unedited.** Its `:root` and `.dark` blocks beat the pack. The rest is Tailwind build syntax a browser ignores.

## By hand

**Web fonts.** A theme names the font. You load it.

**Letter spacing.**

```css
body { letter-spacing: var(--tracking-normal); }
```

## base

```{r}
#| eval: false
bc_deps(style = "base")
```

**Tokens and structure, no visuals.** Where you start a pack, not where you theme one.

## Your own Tailwind

**Load it before `bc_deps()`.** After resets borders and inputs.
